Pesticides pollution of small streams in Germany

### 2016-07-25 article.tex
first commit on new pc

We used Multidimensional Scaling (MDS) based on jeccard dissimilarity in conjunction with hierarchical clustering to display differences in the spectra of analysed compounds per federal state.

>>>>

We used Multidimensional Scaling (MDS) based on jaccard dissimilarity in conjunction with hierarchical clustering to display differences in the spectra of analysed compounds per federal state.
